---
title: "Vignette Title"
author: "Benjamin Leblanc"
date: "`r Sys.Date()`"
# output: pdf_document
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-sides^[A footnote here.]. 

```{r, include=FALSE}
library(Barbouille)
```


```{r, message=FALSE, warning=FALSE}
# Random values
x <- rnorm(2000)
y <- rnorm(2000)
```

```{r, message=FALSE, warning=FALSE}
# Compute angles
a <- 180 * atan2(y, x) / pi
```


You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[Another footnote.].

```{r, echo=FALSE, results='asis'}
  x <- data.frame(
    `long` = c("bottomright", "bottom", "bottomleft", "left", "center", "right", "topleft", "top", "topright"),
    `short`  = c("br", "b", "bl", "l", "c", "r", "tl", "t", "tr"),
    `index`  = 1:9
  )
knitr::kable(x, caption = "Values of the position parameter in `colorLegend`")
```


